---
header-includes: 
  - \thispagestyle{empty}
  - \usepackage{setspace}
  - \setstretch{2}
  - \AtBeginEnvironment{tabular}{\doublespacing}
  - \AtBeginEnvironment{lltable}{\doublespacing}
  - \AtBeginEnvironment{tablenotes}{\doublespacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1.5}}
  - \usepackage{booktabs}

title             : "NP3"
shorttitle        : "NP3"

author: 
  - name          : "Dion T. Henare"
    affiliation   : "1"
    corresponding : yes
    address       : "Gutenbergstraße 18, 35032 Marburg"
    email         : "dion.henare@uni-marburg.de"
  - name          : "Jan Tunnermann"
    affiliation   : "1"
  - name          : "Anna Schuboe"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Philipps-University of Marburg, Germany"

author_note: |
  Funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) – project number 222641018 – SFB/TRR 135 TP B3

abstract: |
  Abstract goes here

bibliography      : ["NP32019_references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

numbersection     : no
class             : "man"
output            : papaja::apa6_pdf

---

\raggedbottom

```{r setup, include = FALSE}
set.seed(4609948)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
library(knitr)
opts_chunk$set(echo = FALSE)
library("papaja")
library(tidyr)
library(dplyr)
library(ggplot2)
library(afex)
library(xtable)
library(RColorBrewer)
library(emmeans)
```

# Introduction

# Methods

# Results

## Behavioural results
```{r organiseBehavData}
behavData <- read.table("Behaviour/BehavData.csv",header = TRUE, sep=",")

#Remove lots of the default EPrime columns
behavData <- select(behavData,-c(ExperimentName	,Session	,Clock.Information	,DataFile.Basename	,Display.RefreshRate	,ExperimentVersion	,PracAcc	,PracRT	,RandomSeed	,RuntimeCapabilities	,RuntimeVersion	,RuntimeVersionExpected	,SessionDate	,SessionStartDateTimeUtc	,SessionTime	,StudioVersion	,totalEuro	,totalPoints	,FiveDiffLeftFar	,FiveDiffLeftNear	,FiveDiffRightFar	,FiveDiffRightNear	,FiveEasyLeftFar	,FiveEasyLeftNear	,FiveEasyRightFar	,FiveEasyRightNear	,FourDiffLeftFar	,FourDiffLeftNear	,FourDiffRightFar	,FourDiffRightNear	,FourEasyLeftFar	,FourEasyLeftNear	,FourEasyRightFar	,FourEasyRightNear	,image1x	,image1y	,image2x	,image2y	,image3x	,image3y	,image4x	,image4y	,image5x	,image5y	,image6x	,image6y	,image7x	,image7y	,image8x	,image8y	,leftImage1	,leftImage2	,leftImage3	,leftImage4	,leftImage5	,leftImage6	,leftImage7	,leftImage8	,OneDiffLeftFar	,OneDiffLeftNear	,OneDiffRightFar	,OneDiffRightNear	,OneEasyLeftFar	,OneEasyLeftNear	,OneEasyRightFar	,OneEasyRightNear	,Response.ACC	,Response.CRESP	,Response.DurationError	,Response.OnsetDelay	,Response.OnsetTime	,Response.OnsetToOnsetTime	,Response.RESP	,Response.RT	,Response.RTTime	,Response1.ACC	,Response1.CRESP	,Response1.DurationError	,Response1.OnsetDelay	,Response1.OnsetTime	,Response1.OnsetToOnsetTime	,Response1.RESP	,Response1.RT	,Response1.RTTime	,rightImage1	,rightImage2	,rightImage3	,rightImage4	,rightImage5	,rightImage6	,rightImage7	,rightImage8	,Search.DurationError	,Search.OffsetTime	,Search.OnsetDelay	,Search.OnsetTime	,SevenDiffLeftFar	,SevenDiffLeftNear	,SevenDiffRightFar	,SevenDiffRightNear	,SevenEasyLeftFar	,SevenEasyLeftNear	,SevenEasyRightFar	,SevenEasyRightNear	,SixDiffLeftFar	,SixDiffLeftNear	,SixDiffRightFar	,SixDiffRightNear	,SixEasyLeftFar	,SixEasyLeftNear	,SixEasyRightFar	,SixEasyRightNear	,ThreeDiffLeftFar	,ThreeDiffLeftNear	,ThreeDiffRightFar	,ThreeDiffRightNear	,ThreeEasyLeftFar	,ThreeEasyLeftNear	,ThreeEasyRightFar	,ThreeEasyRightNear	,TwoDiffLeftFar	,TwoDiffLeftNear	,TwoDiffRightFar	,TwoDiffRightNear	,TwoEasyLeftFar	,TwoEasyLeftNear	,TwoEasyRightFar	,TwoEasyRightNear	)
       )
#Remove practice trials
behavData <- filter(behavData, Running.Block. != "Practice")

#Make subejct a factor
behavData$Subject <- as.factor(behavData$Subject)

#Reorder the relevant variable factors and make table
behavData$collapseNFLR <- factor(behavData$collapseNFLR, levels = c("One", "Two", "Three", "Four", "Five", "Six", "Seven"))

```

(ref:indvSubjChoice) The proportion of trials where participants chose to respond to the easy target as a function of set size for the easy target. Greater than 50% would indicate a preference for the easy target in that condition, whereas less than 50% would indicate a preference for the difficult target in that condition.

```{r plotIndvSubjChoice, fig.cap="(ref:indvSubjChoice)"}
#Make group RT
groupChoice <- behavData %>%
  mutate(Subject = "Average") %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(numEasy = sum(ChoseEasy), numDiff = sum(ChoseDiff)) %>%
  mutate(totalTrials = numEasy+numDiff) %>%
  mutate(propEasy = numEasy/totalTrials)
#Plot participant choices
behavData %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(numEasy = sum(ChoseEasy), numDiff = sum(ChoseDiff)) %>%
  mutate(totalTrials = numEasy+numDiff) %>%
  mutate(propEasy = numEasy/totalTrials) %>%
  ggplot(., aes(collapseNFLR,propEasy, colour = Subject, group = Subject)) +
  #geom_rect(aes(xmin = 0, xmax = Inf, ymin = 0.5, ymax = 1), fill = "deepskyblue1", alpha = 0.2, colour = NA) +
  #geom_rect(aes(xmin = 0, xmax = Inf, ymin = 0, ymax = .5), fill = "tomato1", colour = NA) +
  geom_line(alpha = 0.5, size = 1) +
  geom_point(data = groupChoice, size = 3.5, color = "black") + 
  geom_line(data = groupChoice, size = 2.5, color = "black") +
  geom_hline(yintercept = 0.5) +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(limits = c(0,1),name ="Proportion of easy target selections", breaks = seq(0, 1, .25)) +
  guides(colour=FALSE, group = FALSE) +
  theme_apa()+
  theme(text= element_text(size=22),axis.line = element_line(color = "black", 
                           size = 1, linetype = "solid"))
stats <- behavData %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(numEasy = sum(ChoseEasy), numDiff = sum(ChoseDiff)) %>%
  mutate(totalTrials = numEasy+numDiff) %>%
  mutate(propEasy = numEasy/totalTrials)
contrasts(stats$collapseNFLR) <- contr.poly(7)
result <- lm(propEasy ~ 1 + collapseNFLR, data = stats)
round(summary(result)$coefficients,3)
```

(ref:indvSubjAcc) Participant accuracy as a fucntion of easy target set size.

```{r plotIndvSubjAccuracy, fig.cap="(ref:indvSubjAcc)"}
#Make group acc
groupAcc <- behavData %>%
  mutate(Subject = "Average", Search.ACC = Search.ACC*100) %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(Accuracy = mean(Search.ACC))
behavData %>%
  mutate(Search.ACC = Search.ACC*100) %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(Accuracy = mean(Search.ACC)) %>%
  ggplot(., aes(collapseNFLR,Accuracy, colour = Subject, group = Subject)) +
  geom_line(alpha = 0.5) + 
  geom_point(data = groupAcc, size = 2.5, color = "black") +
  geom_line(data = groupAcc, size = 1.5, color = "black") +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Accuracy (%)", limits = c(50,100)) +
  guides(colour=FALSE, group = FALSE) +
  theme_apa()
stats <- behavData %>%
  mutate(Search.ACC = Search.ACC*100) %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(Accuracy = mean(Search.ACC))
contrasts(stats$collapseNFLR) <- contr.poly(7)
result <- lm(Accuracy ~ 1 + collapseNFLR, data = stats)
round(summary(result)$coefficients,3)
```

(ref:indvSubjRT) Participants response time as a function of set size for the easy target.

```{r plotIndvSubjRT, fig.cap="(ref:indvSubjRT)"}
#Make group RT
groupRT <- behavData %>%
  filter(Search.ACC == 1) %>%
  mutate(Subject = "Average") %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(RT = mean(Search.RT)) %>%
  mutate(RT= ifelse(RT==0,NA,RT))
behavData %>%
  filter(Search.ACC == 1) %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(RT = mean(Search.RT)) %>%
  mutate(RT= ifelse(RT==0,NA,RT)) %>%
  ggplot(., aes(collapseNFLR,RT, colour = Subject, group = Subject)) +
  geom_line(alpha = 0.5) +
  geom_point(data = groupRT, size = 2.5, color = "black") +
  geom_line(data = groupRT, size = 1.5, color = "black") +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Response time (ms)", limits = c(500,1000)) +
  guides(colour=FALSE, group = FALSE) +
  theme_apa()
stats <- behavData %>%
  filter(Search.ACC == 1) %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(RT = mean(Search.RT)) %>%
  mutate(RT= ifelse(RT==0,NA,RT))
contrasts(stats$collapseNFLR) <- contr.poly(7)
result <- lm(RT ~ 1 + collapseNFLR, data = stats)
round(summary(result)$coefficients,3)
```

## ERP results

```{r organiseERPData}
dPath = 'EEG/Visuals/'
fPrefix = 'N2pc'

#####
#Creates aggregate of all participant data (needs dPath and fPrefix)
eFilePattern = paste(fPrefix,"*_epochs.csv", sep="")
lFilePattern = paste(fPrefix,"*_LH.csv", sep="")
rFilePattern = paste(fPrefix,"*_RH.csv", sep="")
eFileList = list.files(dPath, pattern=glob2rx(eFilePattern))
lFileList = list.files(dPath, pattern=glob2rx(lFilePattern))
rFileList = list.files(dPath, pattern=glob2rx(rFilePattern))

#create variables using first dataset
epochInfo = read.csv(file = paste(dPath,eFileList[1], sep=""))
epochInfo$Subject = 1
lHemData = read.csv(file = paste(dPath,lFileList[1], sep=""), header = FALSE)
rHemData = read.csv(file = paste(dPath,rFileList[1], sep=""), header = FALSE)
#append the other datasets to the above variables
for (subj in 2:length(eFileList)) {
  curEpochInfo = read.csv(file = paste(dPath,eFileList[subj], sep=""))
  curEpochInfo$Subject = subj
  curLHemData = read.csv(file = paste(dPath,lFileList[subj], sep=""), header = FALSE)
  curRHemData = read.csv(file = paste(dPath,rFileList[subj], sep=""), header = FALSE)
  
  epochInfo = rbind(epochInfo, curEpochInfo)
  lHemData = rbind(lHemData, curLHemData)
  rHemData = rbind(rHemData, curRHemData)
}

#clear stuff that I don't need
rm(curEpochInfo,curLHemData,curRHemData, fPrefix, eFileList, eFilePattern, lFileList, lFilePattern, rFileList, rFilePattern, subj)
#####
#Permutation can be done at this stage using epochInfo$Hemifield = sample(epochInfo$Hemifield, replace=FALSE)
#combine all the data together into one long table
gathercols = colnames(lHemData)
lHemData$Hem = "Left"
rHemData$Hem = "Right"
scalpData = rbind(lHemData,rHemData)
origEpochInfo = rbind(epochInfo,epochInfo)

allData <- cbind(origEpochInfo, scalpData)
allData <- gather(allData, "sample", "voltage", gathercols, factor_key = TRUE)

#Tidy variable names etc. and create any necessary variables - could use unite
allData$sample <- as.integer(substring(allData$sample,2))
allData <- allData %>% mutate(Hemisphere = ifelse(EasyField==Hem, "Ipsilateral", "Contralateral"))
allData$SimpSet <- allData$EasySet
allData$SimpSet <- recode(allData$SimpSet, "1" = "Small", "2" = "Small", "3" ="Medium", "4"="Medium", "5"="Medium", "6"="Large", "7"="Large")

#clear stuff that I don't need
rm(origEpochInfo,scalpData)
```

```{r setParams}
baseline = 200
srateMultiplier = 2
winSize = 50
winBnd <- 0.8
fixedWin=1


subjRej <- allData %>%
    filter(Event == "Search",sample == 1, Hemisphere == 'Contralateral') %>%
    group_by(Subject) %>%
    summarise(trialCount = sum(sample)) %>%
  mutate(rej = ifelse(trialCount < 600,1,0))
for (i in unique(allData$Subject)) {
  allData$rej[allData$Subject == i] = subjRej$rej[subjRej$Subject==i]
}
```

```{r grandAverageERP}
allData %>%
  filter(Event == "Search" & rej == 0) %>%
  mutate(sample = sample*srateMultiplier-baseline) %>%
  group_by(sample,Hemisphere) %>%
  summarise(mean = mean(voltage)) %>%
  spread(Hemisphere, mean) %>% 
  mutate(diff = Contralateral - Ipsilateral) %>%
  ggplot(., aes(sample, diff)) +
  geom_line() +
  scale_x_continuous(name ="Latency (ms)", expand = c(0, 0)) +
    scale_y_reverse(name =expression(paste("Amplitude (",mu,"v)")), expand = c(0, 0)) +
    geom_vline(xintercept = 0,linetype = "dashed" ) +
    geom_hline(yintercept = 0,linetype = "dashed") +
    theme_apa() +
    theme(panel.spacing.y = unit(2, "lines"), text= element_text(size=12))
```

### N2pc

```{r N2pcStats}
grandAverage <- allData %>%
  filter(Event == "Search" & rej == 0) %>%
  mutate(sample = sample*srateMultiplier-baseline) %>%
  filter(sample > 180, sample < 350) %>%
  group_by(sample,Hemisphere) %>%
  summarise(mean = mean(voltage)) %>%
  spread(Hemisphere, mean) %>% 
  mutate(diff = Contralateral - Ipsilateral)
if (fixedWin) {
  N2pcStart = grandAverage$sample[grandAverage$diff == min(grandAverage$diff)]-winSize/2
  N2pcEnd = grandAverage$sample[grandAverage$diff == min(grandAverage$diff)]+winSize/2
} else {
  peakTime <- grandAverage$sample[grandAverage$diff == min(grandAverage$diff)]
  peakValue <- min(grandAverage$diff)
  N2pcStart <- grandAverage$sample[max(which(grandAverage[1:which(grandAverage$sample==peakTime)-1,]$diff>peakValue*winBnd))]
  postPeakData <- grandAverage[which(grandAverage$sample==peakTime)+1:nrow(grandAverage),]
  N2pcEnd <- postPeakData$sample[min(which(postPeakData$diff > peakValue*winBnd))]
}
N2pc.data <- allData %>%
  mutate(sample = sample*2-baseline) %>%
  filter(Event == "Search" & sample>N2pcStart & sample < N2pcEnd, rej == 0) %>%
  group_by(EasySet,Hemisphere,Subject) %>%
  summarise(mV = mean(voltage)) %>%
  spread(Hemisphere,mV) %>%
  mutate(diff = Contralateral - Ipsilateral)
#plot values
N2pc.data %>%
  group_by(EasySet) %>%
  summarise(diff = mean(diff)) %>%
  ggplot(., aes(x = EasySet, y = diff)) +
  geom_point()
ggplot(N2pc.data, aes(x = EasySet, y = diff)) +
  geom_point()
N2pc.data$EasySet <- as.factor(N2pc.data$EasySet)
contrasts(N2pc.data$EasySet) <- contr.poly(7)
result <- lm(diff ~ 1 + EasySet, data = N2pc.data)
round(summary(result)$coefficients,3)
```

### P1pc

```{r P1pcStats}
grandAverage <- allData %>%
  filter(Event == "Search" & rej == 0) %>%
  mutate(sample = sample*srateMultiplier-baseline) %>%
  filter(sample > 0, sample < 200) %>%
  group_by(sample,Hemisphere) %>%
  summarise(mean = mean(voltage)) %>%
  spread(Hemisphere, mean) %>% 
  mutate(diff = Contralateral - Ipsilateral)
if (fixedWin) {
  P1pcStart = grandAverage$sample[grandAverage$diff == max(grandAverage$diff)]-winSize/2
  P1pcEnd = grandAverage$sample[grandAverage$diff == max(grandAverage$diff)]+winSize/2
} else {
  peakTime <- grandAverage$sample[grandAverage$diff == min(grandAverage$diff)]
  peakValue <- min(grandAverage$diff)
  P1pcStart <- grandAverage$sample[max(which(grandAverage[1:which(grandAverage$sample==peakTime)-1,]$diff>peakValue*winBnd))]
  postPeakData <- grandAverage[which(grandAverage$sample==peakTime)+1:nrow(grandAverage),]
  P1pcEnd <- postPeakData$sample[min(which(postPeakData$diff > peakValue*winBnd))]
}
P1pc.data <- allData %>%
  mutate(sample = sample*2-baseline) %>%
  filter(Event == "Search" & sample>P1pcStart & sample < P1pcEnd, rej == 0) %>%
  group_by(EasySet,Hemisphere,Subject) %>%
  summarise(mV = mean(voltage)) %>%
  spread(Hemisphere,mV) %>%
  mutate(diff = Contralateral - Ipsilateral)
#plot values
P1pc.data %>%
  group_by(EasySet) %>%
  summarise(diff = mean(diff)) %>%
  ggplot(., aes(x = EasySet, y = diff)) +
  geom_point()
ggplot(P1pc.data, aes(x = EasySet, y = diff)) +
  geom_point()
P1pc.data$EasySet <- as.factor(P1pc.data$EasySet)
contrasts(P1pc.data$EasySet) <- contr.poly(7)
result <- lm(diff ~ 1 + EasySet, data = P1pc.data)
round(summary(result)$coefficients,3)
```

### SPCN

```{r SPCNStats}
SPCNStart = 300
SPCNEnd = 600

SPCN.data <- allData %>%
  mutate(sample = sample*2-baseline) %>%
  filter(Event == "Search" & sample>SPCNStart & sample < SPCNEnd, rej == 0) %>%
  group_by(EasySet,Hemisphere,Subject) %>%
  summarise(mV = mean(voltage)) %>%
  spread(Hemisphere,mV) %>%
  mutate(diff = Contralateral - Ipsilateral)
#plot values
SPCN.data %>%
  group_by(EasySet) %>%
  summarise(diff = mean(diff)) %>%
  ggplot(., aes(x = EasySet, y = diff)) +
  geom_point()
ggplot(SPCN.data, aes(x = EasySet, y = diff)) +
  geom_point()
SPCN.data$EasySet <- as.factor(SPCN.data$EasySet)
contrasts(SPCN.data$EasySet) <- contr.poly(7)
result <- lm(diff ~ 1 + EasySet, data = SPCN.data)
round(summary(result)$coefficients,3)
```

(ref:fullSetERPCap) Subtractracted ERPs showing the lateralized response contralateral to the side of the easy target as a function of easy set size. Component windows are highlighted.


```{r fullSetPlot, fig.cap="(ref:fullSetERPCap)"}
my_palette <- brewer.pal(name="Blues",n=9)[3:9]
#Subtracted ERPs split by all set sizes
allData %>%
  filter(Event == "Search", rej == 0) %>%
  mutate(sample = sample*2-baseline, EasySet = as.factor(EasySet)) %>%
  group_by(EasySet,sample,Hemisphere) %>%
  summarise(mean = mean(voltage)) %>%
  spread(Hemisphere, mean) %>% 
  mutate(diff = Contralateral - Ipsilateral) %>%
  ggplot(., aes(sample,diff)) +
    geom_rect(xmin = P1pcStart, xmax = P1pcEnd, ymin = -Inf, ymax = 0, fill = "lemonchiffon") +
    geom_rect(xmin = N2pcStart, xmax = N2pcEnd, ymin = Inf, ymax = 0, fill = "lemonchiffon") +
    geom_rect(xmin = SPCNStart, xmax = SPCNEnd, ymin = Inf, ymax = 0, fill = "lemonchiffon") +
    geom_line(aes(colour = EasySet),size=1) +
    scale_color_manual(values = my_palette) +
    scale_x_continuous(name ="Latency (ms)", expand = c(0, 0)) +
    scale_y_reverse(name =expression(paste("Amplitude (",mu,"v)")), expand = c(0, 0)) +
    geom_vline(xintercept = 0,linetype = "dashed" ) +
    geom_hline(yintercept = 0,linetype = "dashed") +
    theme_apa() +
    theme(panel.spacing.y = unit(2, "lines"), text= element_text(size=12))
```

# Discussion

\newpage

```{r create_r-references}
r_refs(file = "NP32019_references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
