---
header-includes: 
  - \thispagestyle{empty}
  - \usepackage{setspace}
  - \setstretch{2}
  - \AtBeginEnvironment{tabular}{\doublespacing}
  - \AtBeginEnvironment{lltable}{\doublespacing}
  - \AtBeginEnvironment{tablenotes}{\doublespacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1.5}}
  - \usepackage{booktabs}

title             : "NP3"
shorttitle        : "NP3"

author: 
  - name          : "Dion T. Henare"
    affiliation   : "1"
    corresponding : yes
    address       : "Gutenbergstraße 18, 35032 Marburg"
    email         : "dion.henare@uni-marburg.de"
  - name          : "Jan Tunnermann"
    affiliation   : "1"
  - name          : "Anna Schuboe"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Philipps-University of Marburg, Germany"

author_note: |
  Funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) – project number 222641018 – SFB/TRR 135 TP B3

abstract: |
  Abstract goes here

bibliography      : ["NP32019_references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

numbersection     : no
class             : "man"
output            : papaja::apa6_pdf

---

\raggedbottom

```{r setup, include = FALSE}
set.seed(4609948)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
library(knitr)
opts_chunk$set(echo = FALSE)
library("papaja")
library(tidyr)
library(dplyr)
library(ggplot2)
library(afex)
library(xtable)
library(RColorBrewer)
```

```{r organiseBehavData}
behavData <- read.table("Behaviour/BehavData.csv",header = TRUE, sep=",")

#Remove lots of the default EPrime columns
behavData <- select(behavData,-c(ExperimentName	,Session	,Clock.Information	,DataFile.Basename	,Display.RefreshRate	,ExperimentVersion	,PracAcc	,PracRT	,RandomSeed	,RuntimeCapabilities	,RuntimeVersion	,RuntimeVersionExpected	,SessionDate	,SessionStartDateTimeUtc	,SessionTime	,StudioVersion	,totalEuro	,totalPoints	,FiveDiffLeftFar	,FiveDiffLeftNear	,FiveDiffRightFar	,FiveDiffRightNear	,FiveEasyLeftFar	,FiveEasyLeftNear	,FiveEasyRightFar	,FiveEasyRightNear	,FourDiffLeftFar	,FourDiffLeftNear	,FourDiffRightFar	,FourDiffRightNear	,FourEasyLeftFar	,FourEasyLeftNear	,FourEasyRightFar	,FourEasyRightNear	,image1x	,image1y	,image2x	,image2y	,image3x	,image3y	,image4x	,image4y	,image5x	,image5y	,image6x	,image6y	,image7x	,image7y	,image8x	,image8y	,leftImage1	,leftImage2	,leftImage3	,leftImage4	,leftImage5	,leftImage6	,leftImage7	,leftImage8	,OneDiffLeftFar	,OneDiffLeftNear	,OneDiffRightFar	,OneDiffRightNear	,OneEasyLeftFar	,OneEasyLeftNear	,OneEasyRightFar	,OneEasyRightNear	,Response.ACC	,Response.CRESP	,Response.DurationError	,Response.OnsetDelay	,Response.OnsetTime	,Response.OnsetToOnsetTime	,Response.RESP	,Response.RT	,Response.RTTime	,Response1.ACC	,Response1.CRESP	,Response1.DurationError	,Response1.OnsetDelay	,Response1.OnsetTime	,Response1.OnsetToOnsetTime	,Response1.RESP	,Response1.RT	,Response1.RTTime	,rightImage1	,rightImage2	,rightImage3	,rightImage4	,rightImage5	,rightImage6	,rightImage7	,rightImage8	,Search.DurationError	,Search.OffsetTime	,Search.OnsetDelay	,Search.OnsetTime	,SevenDiffLeftFar	,SevenDiffLeftNear	,SevenDiffRightFar	,SevenDiffRightNear	,SevenEasyLeftFar	,SevenEasyLeftNear	,SevenEasyRightFar	,SevenEasyRightNear	,SixDiffLeftFar	,SixDiffLeftNear	,SixDiffRightFar	,SixDiffRightNear	,SixEasyLeftFar	,SixEasyLeftNear	,SixEasyRightFar	,SixEasyRightNear	,ThreeDiffLeftFar	,ThreeDiffLeftNear	,ThreeDiffRightFar	,ThreeDiffRightNear	,ThreeEasyLeftFar	,ThreeEasyLeftNear	,ThreeEasyRightFar	,ThreeEasyRightNear	,TwoDiffLeftFar	,TwoDiffLeftNear	,TwoDiffRightFar	,TwoDiffRightNear	,TwoEasyLeftFar	,TwoEasyLeftNear	,TwoEasyRightFar	,TwoEasyRightNear	)
       )
#Remove practice trials
behavData <- filter(behavData, Running.Block. != "Practice")

#Make subejct a factor
behavData$Subject <- as.factor(behavData$Subject)

#Reorder the relevant variable factors and make table
behavData$collapseNFLR <- factor(behavData$collapseNFLR, levels = c("One", "Two", "Three", "Four", "Five", "Six", "Seven"))
```

(ref:indvSubjChoice) The proportion of trials where participants chose to respond to the easy target as a function of set size for the easy target. Greater than 50% would indicate a preference for the easy target in that condition, whereas less than 50% would indicate a preference for the difficult target in that condition.

```{r plotIndvSubjChoice, fig.cap="(ref:indvSubjChoice)"}
#Make group RT
groupChoice <- behavData %>%
  mutate(Subject = "Average") %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(numEasy = sum(ChoseEasy), numDiff = sum(ChoseDiff)) %>%
  mutate(totalTrials = numEasy+numDiff) %>%
  mutate(propEasy = numEasy/totalTrials)
#Plot participant choices
behavData %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(numEasy = sum(ChoseEasy), numDiff = sum(ChoseDiff)) %>%
  mutate(totalTrials = numEasy+numDiff) %>%
  mutate(propEasy = numEasy/totalTrials) %>%
  ggplot(., aes(collapseNFLR,propEasy, colour = Subject, group = Subject)) +
  geom_line(alpha = 0.5) +
  geom_point(data = groupChoice, size = 2.5, color = "black") + 
  geom_line(data = groupChoice, size = 1.5, color = "black") +
  geom_hline(yintercept = 0.5) +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Proportion of easy target selections") +
  theme_apa()
```

(ref:indvSubjAcc) Participant accuracy as a fucntion of set size for the easy target.

```{r plotIndvSubjAccuracy, fig.cap="(ref:indvSubjAcc)"}
#Make group acc
groupAcc <- behavData %>%
  mutate(Subject = "Average", Search.ACC = Search.ACC*100) %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(Accuracy = mean(Search.ACC))
behavData %>%
  mutate(Search.ACC = Search.ACC*100) %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(Accuracy = mean(Search.ACC)) %>%
  ggplot(., aes(collapseNFLR,Accuracy, colour = Subject, group = Subject)) +
  geom_line(alpha = 0.5) + 
  geom_point(data = groupAcc, size = 2.5, color = "black") +
  geom_line(data = groupAcc, size = 1.5, color = "black") +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Accuracy (%)") +
  theme_apa()
```

(ref:indvSubjRT) Participants response time as a function of set size for the easy target.

```{r plotIndvSubjRT, fig.cap="(ref:indvSubjRT)"}
#Make group RT
groupRT <- behavData %>%
  mutate(Subject = "Average") %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(RT = mean(Search.RT))
behavData %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(RT = mean(Search.RT)) %>%
  ggplot(., aes(collapseNFLR,RT, colour = Subject, group = Subject)) +
  geom_line(alpha = 0.5) +
  geom_point(data = groupRT, size = 2.5, color = "black") +
  geom_line(data = groupRT, size = 1.5, color = "black") +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Response time (ms)") +
  theme_apa()
```

```{r organiseData}
dPath = 'EEG/Visuals/'
fPrefix = 'N2pc'

#####
#Creates aggregate of all participant data (needs dPath and fPrefix)
eFilePattern = paste(fPrefix,"*_epochs.csv", sep="")
lFilePattern = paste(fPrefix,"*_LH.csv", sep="")
rFilePattern = paste(fPrefix,"*_RH.csv", sep="")
eFileList = list.files(dPath, pattern=glob2rx(eFilePattern))
lFileList = list.files(dPath, pattern=glob2rx(lFilePattern))
rFileList = list.files(dPath, pattern=glob2rx(rFilePattern))

#create variables using first dataset
epochInfo = read.csv(file = paste(dPath,eFileList[1], sep=""))
epochInfo$Subject = 1
lHemData = read.csv(file = paste(dPath,lFileList[1], sep=""), header = FALSE)
rHemData = read.csv(file = paste(dPath,rFileList[1], sep=""), header = FALSE)
#append the other datasets to the above variables
for (subj in 2:length(eFileList)) {
  curEpochInfo = read.csv(file = paste(dPath,eFileList[subj], sep=""))
  curEpochInfo$Subject = subj
  curLHemData = read.csv(file = paste(dPath,lFileList[subj], sep=""), header = FALSE)
  curRHemData = read.csv(file = paste(dPath,rFileList[subj], sep=""), header = FALSE)
  
  epochInfo = rbind(epochInfo, curEpochInfo)
  lHemData = rbind(lHemData, curLHemData)
  rHemData = rbind(rHemData, curRHemData)
}

#clear stuff that I don't need
rm(curEpochInfo,curLHemData,curRHemData, fPrefix, eFileList, eFilePattern, lFileList, lFilePattern, rFileList, rFilePattern, subj)
#####
#Permutation can be done at this stage using epochInfo$Hemifield = sample(epochInfo$Hemifield, replace=FALSE)
#combine all the data together into one long table
gathercols = colnames(lHemData)
lHemData$Hem = "Left"
rHemData$Hem = "Right"
scalpData = rbind(lHemData,rHemData)
origEpochInfo = rbind(epochInfo,epochInfo)

allData <- cbind(origEpochInfo, scalpData)
allData <- gather(allData, "sample", "voltage", gathercols, factor_key = TRUE)

#Tidy variable names etc. and create any necessary variables - could use unite
allData$sample <- as.integer(substring(allData$sample,2))
allData <- allData %>% mutate(Hemisphere = ifelse(EasyField==Hem, "Ipsilateral", "Contralateral"))
allData$SimpSet <- allData$EasySet
allData$SimpSet <- recode(allData$SimpSet, "1" = "Small", "2" = "Small", "3" ="Medium", "4"="Medium", "5"="Medium", "6"="Large", "7"="Large")

#clear stuff that I don't need
rm(origEpochInfo,scalpData)
```

```{r setParams}
baseline = 200
plotWidth = 24
plotHeight = 9

N2pcStart = 200
N2pcEnd = 300
SPCNStart = 300
SPCNEnd = 498
```

```{r countTrials, results='asis'}
print(
  xtable(allData %>%
    filter(Event == "Search",sample == 1, Hemisphere == 'Contralateral') %>%
    group_by(Subject,SimpSet) %>%
    summarise(trialCount = sum(sample)) %>%
      spread(SimpSet,trialCount)
  ,digits = 0)
,include.rownames = FALSE, comment = FALSE)
```

```{r ERPStats, warning=FALSE}
N2pc.data <- allData %>%
  mutate(sample = sample*2-baseline) %>%
  filter(Event == "Search" & sample>N2pcStart & sample < N2pcEnd) %>%
  group_by(SimpSet,Hemisphere,Subject) %>%
  summarise(mV = mean(voltage))
N2pc.aov <- aov_ez(
  data = N2pc.data,
  dv = "mV",
  id = "Subject", 
  within = c("Hemisphere","SimpSet")
)
N2pc.results <- apa_print(N2pc.aov)

SPCN.data <- allData %>%
  mutate(sample = sample*2-baseline) %>%
  filter(Event == "Search" & sample>SPCNStart & sample < SPCNEnd) %>%
  group_by(SimpSet,Hemisphere,Subject) %>%
  summarise(mV = mean(voltage))
SPCN.aov <- aov_ez(
  data = SPCN.data,
  dv = "mV",
  id = "Subject", 
  within = c("Hemisphere","SimpSet")
)
SPCN.results <- apa_print(SPCN.aov)

#Extract for SPSS
ExportN2pc <- N2pc.data %>% unite(Condition,c("SimpSet","Hemisphere")) %>% spread(Condition,mV)
write.csv(ExportN2pc,"EEG\\N2pcStats.csv", row.names = FALSE)
ExportSPCN <- SPCN.data %>% unite(Condition,c("SimpSet","Hemisphere")) %>% spread(Condition,mV)
write.csv(ExportSPCN,"EEG\\SPCNStats.csv", row.names = FALSE)
```

The results of the interaction in the 2x3 (electrode by simplified set size) ANOVA for N2pc amplitude (`r N2pc.results$full_result$Hemisphere_SimpSet`).

```{r N2pcStatsTable, results='asis'}
apa_table(
  N2pc.results$table
  , caption = "Results of the 2x3 repeated measures ANOVA (Hemisphere by simplified set size) for the N2pc component."
  , note = "Note goes here."
)
```

The results of the interaction in the 2x3 (electrode by simplified set size) ANOVA for SPCN amplitude (`r SPCN.results$full_result$Hemisphere_SimpSet`).

```{r SPCNStatsTable, results='asis'}
apa_table(
  SPCN.results$table
  , caption = "Results of the 2x3 repeated measures ANOVA (Hemisphere by simplified set size) for the SPCN component."
  , note = "Note goes here."
)
```

(ref:fullSetERPCap) Subtractracted ERPs showing the lateralized response contralateral to the side of the easy target as a function of easy set size.

```{r fullSetPlot, fig.cap="(ref:fullSetERPCap)"}
#Subtracted ERPs split by all set sizes
allData %>%
  filter(Event == "Search") %>%
  mutate(sample = sample*2-baseline) %>%
  group_by(EasySet,sample,Hemisphere) %>%
  summarise(mean = mean(voltage)) %>%
  spread(Hemisphere, mean) %>% 
  mutate(diff = Contralateral - Ipsilateral) %>%
  ggplot(., aes(sample,diff)) +
    geom_line(aes(colour = EasySet),size=1) +
    scale_colour_brewer(palette = "Blues") +
    scale_x_continuous(name ="Latency (ms)", expand = c(0, 0)) +
    scale_y_reverse(name =expression(paste("Amplitude (",mu,"v)")), expand = c(0, 0)) +
    geom_vline(xintercept = 0,linetype = "dashed" ) +
    geom_hline(yintercept = 0,linetype = "dashed") +
    theme_minimal() +
    theme(panel.spacing.y = unit(2, "lines"), text= element_text(size=12))
```

(ref:simpSetUnsubERPCap) Subtractracted ERPs showing the lateralized response contralateral to the side of the easy target as a function of easy set size.

```{r simpSetUnsubPlot, fig.cap="(ref:simpSetUnsubERPCap)"}
#Subtracted ERPs split by all set sizes
allData %>%
  filter(Event == "Search") %>%
  mutate(sample = sample*2-baseline) %>%
  group_by(SimpSet,sample,Hemisphere) %>%
  summarise(mean = mean(voltage)) %>%
  ggplot(., aes(sample,mean)) +
    geom_line(aes(colour = Hemisphere),size=1) +
    scale_colour_brewer(palette = "Set1") +
    scale_x_continuous(name ="Latency (ms)", expand = c(0, 0)) +
    scale_y_reverse(name =expression(paste("Amplitude (",mu,"v)")), expand = c(0, 0)) +
    geom_vline(xintercept = 0,linetype = "dashed" ) +
    geom_hline(yintercept = 0,linetype = "dashed") +
    facet_grid(.~SimpSet) +
    theme_minimal() +
    theme(panel.spacing.y = unit(2, "lines"), text= element_text(size=12))
```

(ref:simpSetERPCap) Subtractracted ERPs showing the lateralized response contralateral to the side of the easy target as a function of easy set size (small=1/2, medium=3/4/5, large = 6/7).

```{r simpSetPlot, fig.cap="(ref:simpSetERPCap)"}
#Uses implified set sizes (1/2 vs 3/4/5 vs 6/7)
my_palette <- brewer.pal(name="Blues",n=9)[4:9]
allData %>%
  filter(Event == "Search") %>%
  mutate(sample = sample*2-baseline) %>%
  group_by(SimpSet,sample,Hemisphere) %>%
  summarise(mean = mean(voltage)) %>%
  spread(Hemisphere, mean) %>% 
  mutate(diff = Contralateral - Ipsilateral) %>%
  ggplot(., aes(sample,diff)) +
    geom_rect(aes(xmin = N2pcStart, xmax = N2pcEnd, ymin = 0, ymax = -1), fill = "mistyrose") +
    geom_line(aes(colour = SimpSet),size=1) +
    labs(colour = "Easy Set Size") +
    scale_color_manual(values = my_palette) +
    scale_x_continuous(name ="Latency (ms)", expand = c(0, 0)) +
    scale_y_reverse(name = expression(paste("Amplitude (",mu,"v)")), expand = c(0, 0)) +
    geom_vline(xintercept = 0,linetype = "dashed" ) +
    geom_hline(yintercept = 0,linetype = "dashed") +
    theme_minimal() +
    theme(panel.spacing.y = unit(2, "lines"), text = element_text(size=12))
```

```{r PPT_simpSetPlot, include = FALSE}
#Create unsubtracted ERPs without component shaded
allData %>%
  filter(Event == "Search") %>%
  mutate(sample = sample*2-baseline) %>%
  group_by(SimpSet,sample,Hemisphere) %>%
  summarise(mean = mean(voltage)) %>%
  ggplot(., aes(sample,mean)) +
    geom_line(aes(colour = Hemisphere),size=2) +
    scale_colour_brewer(palette = "Set1") +
    scale_x_continuous(name ="Latency (ms)", expand = c(0, 0)) +
    scale_y_reverse(name =expression(paste("Amplitude (",mu,"v)")), expand = c(0, 0)) +
    geom_vline(xintercept = 0,linetype = "dashed" ) +
    geom_hline(yintercept = 0,linetype = "dashed") +
    facet_grid(.~SimpSet) +
    theme_minimal() +
    theme(panel.spacing.x = unit(2, "lines"), text= element_text(size=40))
ggsave("unsubSetSizeERPs.pdf",width = plotWidth, height = plotHeight*0.66)
#With component shaded
allData %>%
  filter(Event == "Search") %>%
  mutate(sample = sample*2-baseline) %>%
  group_by(SimpSet,sample,Hemisphere) %>%
  summarise(mean = mean(voltage)) %>%
  ggplot(., aes(sample,mean)) +
    geom_rect(aes(xmin = N2pcStart, xmax = N2pcEnd, ymin = 3, ymax = -9), fill = "mistyrose") +
    geom_line(aes(colour = Hemisphere),size=2) +
    scale_colour_brewer(palette = "Set1") +
    scale_x_continuous(name ="Latency (ms)", expand = c(0, 0)) +
    scale_y_reverse(name =expression(paste("Amplitude (",mu,"v)")), expand = c(0, 0)) +
    geom_vline(xintercept = 0,linetype = "dashed" ) +
    geom_hline(yintercept = 0,linetype = "dashed") +
    facet_grid(.~SimpSet) +
    theme_minimal() +
    theme(panel.spacing.x = unit(2, "lines"), text= element_text(size=40))
ggsave("unsubSetSizeERPsshaded.pdf",width = plotWidth, height = plotHeight*0.66)

my_palette <- brewer.pal(name="Blues",n=9)[4:9]

#Creates and saves a powerpoint friendly version of the above plot split lines
allData %>%
  filter(Event == "Search") %>%
  mutate(sample = sample*2-baseline) %>%
  group_by(SimpSet,sample,Hemisphere) %>%
  summarise(mean = mean(voltage)) %>%
  spread(Hemisphere, mean) %>% 
  mutate(diff = Contralateral - Ipsilateral) %>%
  ggplot(., aes(sample,diff)) +
    geom_rect(aes(xmin = N2pcStart, xmax = N2pcEnd, ymin = 0, ymax = -1), fill = "mistyrose") +
    geom_line(aes(colour = SimpSet),size=5) +
    labs(colour = "Easy Set Size") +
    scale_color_manual(values = my_palette) +
    scale_x_continuous(name ="Latency (ms)", expand = c(0, 0)) +
    scale_y_reverse(name = expression(paste("Amplitude (",mu,"v)")), expand = c(0, 0)) +
    geom_vline(xintercept = 0,linetype = "dashed" ) +
    geom_hline(yintercept = 0,linetype = "dashed") +
    facet_grid(.~SimpSet) +
    theme_minimal() +
    theme(panel.spacing.x = unit(20, "lines"), text = element_text(size=60))
ggsave("simplifiedSetSizeSplitERPs.pdf",width = plotWidth+20, height = plotHeight+5)

#Subtracted split by condition across 3 plots with individual ERPs
allData %>%
  filter(Event == "Search") %>%
  mutate(sample = sample*2-baseline, Subject = as.factor(Subject)) %>%
  group_by(SimpSet,Subject,sample,Hemisphere) %>%
  summarise(mean = mean(voltage)) %>%
  spread(Hemisphere, mean) %>% 
  mutate(diff = Contralateral - Ipsilateral) %>%
  ggplot(., aes(sample,diff)) +
    geom_rect(aes(xmin = N2pcStart, xmax = N2pcEnd, ymin = 0, ymax = -2.5), fill = "mistyrose") +
    geom_line(aes(colour = Subject),size=5) +
    labs(colour = "Easy Set Size") +
    scale_colour_brewer(palette = "Blues") +
    scale_x_continuous(name ="Latency (ms)", expand = c(0, 0)) +
    scale_y_reverse(name = expression(paste("Amplitude (",mu,"v)")), expand = c(0, 0)) +
    geom_vline(xintercept = 0,linetype = "dashed" ) +
    geom_hline(yintercept = 0,linetype = "dashed") +
    facet_grid(.~SimpSet) +
    theme_minimal() +
    theme(panel.spacing.x = unit(20, "lines"), text = element_text(size=60))
ggsave("simplifiedSetSizeSplitERPsIndv.pdf",width = plotWidth+20, height = plotHeight+5)

#Creates and saves a powerpoint friendly version of the above plot
allData %>%
  filter(Event == "Search") %>%
  mutate(sample = sample*2-baseline) %>%
  group_by(SimpSet,sample,Hemisphere) %>%
  summarise(mean = mean(voltage)) %>%
  spread(Hemisphere, mean) %>% 
  mutate(diff = Contralateral - Ipsilateral) %>%
  ggplot(., aes(sample,diff)) +
    geom_rect(aes(xmin = N2pcStart, xmax = N2pcEnd, ymin = 0, ymax = -1), fill = "mistyrose") +
    geom_line(aes(colour = SimpSet),size=5) +
    labs(colour = "Easy Set Size") +
    scale_color_manual(values = my_palette) +
    scale_x_continuous(name ="Latency (ms)", expand = c(0, 0)) +
    scale_y_reverse(name = expression(paste("Amplitude (",mu,"v)")), expand = c(0, 0)) +
    geom_vline(xintercept = 0,linetype = "dashed" ) +
    geom_hline(yintercept = 0,linetype = "dashed") +
    theme_minimal() +
    theme(panel.spacing.y = unit(2, "lines"), text = element_text(size=60))
ggsave("simplifiedSetSizeERPs.pdf",width = plotWidth, height = plotHeight)

#Creates and save powerpoint friendly version of grand mean ERP of all conditions
allData %>%
  filter(Event == "Search") %>%
  mutate(sample = sample*2-baseline) %>%
  group_by(sample,Hemisphere) %>%
  summarise(mean = mean(voltage)) %>%
  spread(Hemisphere, mean) %>% 
  mutate(diff = Contralateral - Ipsilateral) %>%
  ggplot(., aes(sample,diff)) +
    geom_rect(aes(xmin = N2pcStart, xmax = N2pcEnd, ymin = 0, ymax = -1), fill = "mistyrose") +
    geom_line(colour = "Blue",size=5) +
    scale_x_continuous(name ="Latency (ms)", expand = c(0, 0)) +
    scale_y_reverse(name = expression(paste("Amplitude (",mu,"v)")), expand = c(0, 0)) +
    geom_vline(xintercept = 0,linetype = "dashed" ) +
    geom_hline(yintercept = 0,linetype = "dashed") +
    theme_minimal() +
    theme(panel.spacing.y = unit(2, "lines"), text = element_text(size=60))
ggsave("simplifiedSetSizeERPsAvg.pdf",width = plotWidth, height = plotHeight)
```

```{r indvsimpSetPlot, include = FALSE}
#Uses implified set sizes (1/2 vs 3/4/5 vs 6/7)
ERPPlotdata <- allData %>%
  mutate(sample = sample*2-baseline) %>%
  filter(Event == "Search") %>%
  group_by(sample, SimpSet,Hemisphere) %>%
  summarise(mV = mean(voltage))  %>% 
  unite(Condition,c("SimpSet","Hemisphere")) %>% 
  spread(Condition,mV)
write.csv(ERPPlotdata,"EEG\\ERPPlots.csv", row.names = FALSE)
```

\newpage

```{r create_r-references}
r_refs(file = "NP32019_references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
