---
header-includes: 
  - \thispagestyle{empty}
  - \usepackage{setspace}
  - \setstretch{2}
  - \AtBeginEnvironment{tabular}{\doublespacing}
  - \AtBeginEnvironment{lltable}{\doublespacing}
  - \AtBeginEnvironment{tablenotes}{\doublespacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1.5}}
  - \usepackage{booktabs}

title             : "NP3"
shorttitle        : "NP3"

author: 
  - name          : "Dion T. Henare"
    affiliation   : "1"
    corresponding : yes
    address       : "Gutenbergstraße 18, 35032 Marburg"
    email         : "dion.henare@uni-marburg.de"
  - name          : "Jan Tunnermann"
    affiliation   : "1"
  - name          : "Anna Schuboe"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Philipps-University of Marburg, Germany"

author_note: |
  Funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) – project number 222641018 – SFB/TRR 135 TP B3

abstract: |
  Abstract goes here

bibliography      : ["NP32019_references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

numbersection     : no
class             : "man"
output            : papaja::apa6_pdf

---

\raggedbottom

```{r setup, include = FALSE}
set.seed(4609948)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
library(knitr)
opts_chunk$set(echo = FALSE)
library("papaja")
library(tidyr)
library(dplyr)
library(ggplot2)
library(afex)
library(xtable)
library(RColorBrewer)
```

```{r organiseBehavData}
behavData <- read.table("Behaviour/BehavData.csv",header = TRUE, sep=",")

#Remove lots of the default EPrime columns
behavData <- select(behavData,-c(ExperimentName	,Session	,Clock.Information	,DataFile.Basename	,Display.RefreshRate	,ExperimentVersion	,PracAcc	,PracRT	,RandomSeed	,RuntimeCapabilities	,RuntimeVersion	,RuntimeVersionExpected	,SessionDate	,SessionStartDateTimeUtc	,SessionTime	,StudioVersion	,totalEuro	,totalPoints	,FiveDiffLeftFar	,FiveDiffLeftNear	,FiveDiffRightFar	,FiveDiffRightNear	,FiveEasyLeftFar	,FiveEasyLeftNear	,FiveEasyRightFar	,FiveEasyRightNear	,FourDiffLeftFar	,FourDiffLeftNear	,FourDiffRightFar	,FourDiffRightNear	,FourEasyLeftFar	,FourEasyLeftNear	,FourEasyRightFar	,FourEasyRightNear	,image1x	,image1y	,image2x	,image2y	,image3x	,image3y	,image4x	,image4y	,image5x	,image5y	,image6x	,image6y	,image7x	,image7y	,image8x	,image8y	,leftImage1	,leftImage2	,leftImage3	,leftImage4	,leftImage5	,leftImage6	,leftImage7	,leftImage8	,OneDiffLeftFar	,OneDiffLeftNear	,OneDiffRightFar	,OneDiffRightNear	,OneEasyLeftFar	,OneEasyLeftNear	,OneEasyRightFar	,OneEasyRightNear	,Response.ACC	,Response.CRESP	,Response.DurationError	,Response.OnsetDelay	,Response.OnsetTime	,Response.OnsetToOnsetTime	,Response.RESP	,Response.RT	,Response.RTTime	,Response1.ACC	,Response1.CRESP	,Response1.DurationError	,Response1.OnsetDelay	,Response1.OnsetTime	,Response1.OnsetToOnsetTime	,Response1.RESP	,Response1.RT	,Response1.RTTime	,rightImage1	,rightImage2	,rightImage3	,rightImage4	,rightImage5	,rightImage6	,rightImage7	,rightImage8	,Search.DurationError	,Search.OffsetTime	,Search.OnsetDelay	,Search.OnsetTime	,SevenDiffLeftFar	,SevenDiffLeftNear	,SevenDiffRightFar	,SevenDiffRightNear	,SevenEasyLeftFar	,SevenEasyLeftNear	,SevenEasyRightFar	,SevenEasyRightNear	,SixDiffLeftFar	,SixDiffLeftNear	,SixDiffRightFar	,SixDiffRightNear	,SixEasyLeftFar	,SixEasyLeftNear	,SixEasyRightFar	,SixEasyRightNear	,ThreeDiffLeftFar	,ThreeDiffLeftNear	,ThreeDiffRightFar	,ThreeDiffRightNear	,ThreeEasyLeftFar	,ThreeEasyLeftNear	,ThreeEasyRightFar	,ThreeEasyRightNear	,TwoDiffLeftFar	,TwoDiffLeftNear	,TwoDiffRightFar	,TwoDiffRightNear	,TwoEasyLeftFar	,TwoEasyLeftNear	,TwoEasyRightFar	,TwoEasyRightNear	)
       )
#Remove practice trials
behavData <- filter(behavData, Running.Block. != "Practice")

#Make subejct a factor
behavData$Subject <- as.factor(behavData$Subject)

#Reorder the relevant variable factors and make table
behavData$collapseNFLR <- factor(behavData$collapseNFLR, levels = c("One", "Two", "Three", "Four", "Five", "Six", "Seven"))

```

```{r totalTrialNumTable}
behavData %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(numEasy = sum(ChoseEasy), numDiff = sum(ChoseDiff)) %>%
  mutate(totalTrials = numEasy+numDiff) %>%
  select(-c(numEasy,numDiff)) %>%
  spread(collapseNFLR,totalTrials)
```

(ref:indvSubjChoice) The proportion of trials where participants chose to respond to the easy target as a function of set size for the easy target. Greater than 50% would indicate a preference for the easy target in that condition, whereas less than 50% would indicate a preference for the difficult target in that condition.

```{r plotIndvSubjChoice, fig.cap="(ref:indvSubjChoice)"}
#Make group RT
groupChoice <- behavData %>%
  mutate(Subject = "Average") %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(numEasy = sum(ChoseEasy), numDiff = sum(ChoseDiff)) %>%
  mutate(totalTrials = numEasy+numDiff) %>%
  mutate(propEasy = numEasy/totalTrials)
#Plot participant choices
behavData %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(numEasy = sum(ChoseEasy), numDiff = sum(ChoseDiff)) %>%
  mutate(totalTrials = numEasy+numDiff) %>%
  mutate(propEasy = numEasy/totalTrials) %>%
  ggplot(., aes(collapseNFLR,propEasy, colour = Subject, group = Subject)) +
  #geom_rect(aes(xmin = 0, xmax = Inf, ymin = 0.5, ymax = 1), fill = "deepskyblue1", alpha = 0.2, colour = NA) +
  #geom_rect(aes(xmin = 0, xmax = Inf, ymin = 0, ymax = .5), fill = "tomato1", colour = NA) +
  geom_line(alpha = 0.5, size = 1) +
  geom_point(data = groupChoice, size = 3.5, color = "black") + 
  geom_line(data = groupChoice, size = 2.5, color = "black") +
  geom_hline(yintercept = 0.5) +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(limits = c(0,1),name ="Proportion of easy target selections", breaks = seq(0, 1, .25)) +
  guides(colour=FALSE, group = FALSE) +
  theme_apa()+
  theme(text= element_text(size=22),axis.line = element_line(color = "black", 
                           size = 1, linetype = "solid"))
stats <- behavData %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(numEasy = sum(ChoseEasy), numDiff = sum(ChoseDiff)) %>%
  mutate(totalTrials = numEasy+numDiff) %>%
  mutate(propEasy = numEasy/totalTrials)
contrasts(stats$collapseNFLR) <- contr.poly(7)
result <- lm(propEasy ~ 1 + collapseNFLR, data = stats)
round(summary(result)$coefficients,3)
```

(ref:indvSubjAcc) Participant accuracy as a fucntion of easy target set size.

```{r plotIndvSubjAccuracy, fig.cap="(ref:indvSubjAcc)"}
#Make group acc
groupAcc <- behavData %>%
  mutate(Subject = "Average", Search.ACC = Search.ACC*100) %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(Accuracy = mean(Search.ACC))
behavData %>%
  mutate(Search.ACC = Search.ACC*100) %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(Accuracy = mean(Search.ACC)) %>%
  ggplot(., aes(collapseNFLR,Accuracy, colour = Subject, group = Subject)) +
  geom_line(alpha = 0.5) + 
  geom_point(data = groupAcc, size = 2.5, color = "black") +
  geom_line(data = groupAcc, size = 1.5, color = "black") +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Accuracy (%)", limits = c(50,100)) +
  guides(colour=FALSE, group = FALSE) +
  theme_apa()
stats <- behavData %>%
  mutate(Search.ACC = Search.ACC*100) %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(Accuracy = mean(Search.ACC))
contrasts(stats$collapseNFLR) <- contr.poly(7)
result <- lm(Accuracy ~ 1 + collapseNFLR, data = stats)
round(summary(result)$coefficients,3)
```

(ref:groupAccbyChoice) Participant accuracy as a fucntion of easy target set size, separated by whether participants chose to respond to the easy or the difficult target. Shading represents standard error.

```{r accSplitByChoice, fig.cap="(ref:groupAccbyChoice)"}
#Make group acc
behavData %>%
  mutate(Search.ACC = Search.ACC*100, Choice = ifelse(ChoseEasy == 1,"Chose Easy", "Chose Difficult")) %>%
  group_by(collapseNFLR, Choice) %>%
  summarise(mean = mean(Search.ACC), se=sd(Search.ACC)/sqrt(length(Search.ACC))) %>%
  ggplot(., aes(collapseNFLR, mean, colour = Choice, group = Choice)) +
  geom_ribbon(aes(ymin = mean - se, ymax = mean + se, fill = Choice), alpha = 0.2, colour = NA) +
  geom_line(size = 1) +
  scale_color_manual(values=c("royalblue3", "red1"))+
  scale_fill_manual(values=c("royalblue3", "red1"))+
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Accuracy (%)", limits = c(50,100)) +
  theme_apa()
```

(ref:indvAccbyChoice) Participant accuracy as a fucntion of easy target set size, separated by whether participants chose to respond to the easy or the difficult target. Group mean in black and individual subjects plotted behind

```{r indvAccByChoice, fig.cap="(ref:indvAccbyChoice)"}
accData <- behavData %>%
  mutate(Subject = "Average") %>%
  mutate(Search.ACC = Search.ACC*100, Choice = ifelse(ChoseEasy == 1,"Chose Easy", "Chose Difficult")) %>%
  group_by(collapseNFLR, Choice, Subject) %>%
  summarise(Accuracy = mean(Search.ACC)) %>%
  mutate(Accuracy = ifelse(Accuracy==0,NA,Accuracy))
behavData %>%
  mutate(Search.ACC = Search.ACC*100, Choice = ifelse(ChoseEasy == 1,"Chose Easy", "Chose Difficult")) %>%
  group_by(collapseNFLR, Choice, Subject) %>%
  summarise(Accuracy = mean(Search.ACC)) %>%
  mutate(Accuracy = ifelse(Accuracy==0,NA,Accuracy))%>%
  ggplot(., aes(collapseNFLR,Accuracy, colour = Subject, group = Subject)) +
  geom_line(alpha = 0.5) + 
  geom_point(data = accData, size = 2.5, color = "black") + 
  geom_line(data = accData, size = 1.5, color = "black") +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Accuracy (%)") +
  facet_grid(Choice~.) +
  guides(colour=FALSE, group = FALSE) +
  theme_apa()
```

```{r }
accData <- behavData %>%
  mutate(Subject = "Average") %>%
  mutate(Search.ACC = Search.ACC*100, Choice = ifelse(ChoseEasy == 1,"Chose Easy", "Chose Difficult")) %>%
  group_by(collapseNFLR, Choice, Subject) %>%
  summarise(Accuracy = mean(Search.ACC)) %>%
  mutate(Accuracy = ifelse(Accuracy==0,NA,Accuracy))
behavData %>%
  mutate(Search.ACC = Search.ACC*100, Choice = ifelse(ChoseEasy == 1,"Chose Easy", "Chose Difficult")) %>%
  group_by(collapseNFLR, Choice, Subject) %>%
  summarise(Accuracy = mean(Search.ACC)) %>%
  mutate(Accuracy = ifelse(Accuracy==0,NA,Accuracy))%>%
  ggplot(., aes(collapseNFLR,Accuracy, colour = Choice, group = interaction(Subject, Choice))) +
  geom_line(size = 1, alpha = 0.5) + 
  scale_color_manual(values=c("royalblue3", "red1"))+
  geom_point(data = accData, size = 2.5) + 
  geom_line(data = accData, size = 1.5) +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Accuracy (%)") +
  #facet_grid(Choice~.) +
  guides( group = FALSE) +
  theme_apa()

rtData <- behavData %>%
  filter(Search.ACC == 1) %>%
  mutate(Subject = "Average") %>%
  mutate(Choice = ifelse(ChoseEasy == 1,"Chose Easy", "Chose Difficult")) %>%
  group_by(collapseNFLR, Choice, Subject) %>%
  summarise(RT = mean(Search.RT)) %>%
  mutate(RT= ifelse(RT==0,NA,RT))
behavData %>%
  filter(Search.ACC == 1) %>%
  mutate(Choice = ifelse(ChoseEasy == 1,"Chose Easy", "Chose Difficult")) %>%
  group_by(collapseNFLR, Choice, Subject) %>%
  summarise(RT = mean(Search.RT)) %>%
  mutate(RT= ifelse(RT==0,NA,RT)) %>%
  ggplot(., aes(collapseNFLR,RT, colour = Choice, group = interaction(Subject, Choice))) +
  geom_line(size = 1, alpha = 0.5) + 
  scale_color_manual(values=c("royalblue3", "red1"))+
  geom_point(data = rtData, size = 2.5) + 
  geom_line(data = rtData, size = 1.5) +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Accuracy (%)") +
  #facet_grid(Choice~.) +
  guides( group = FALSE) +
  theme_apa()
```

(ref:indvSubjRT) Participants response time as a function of set size for the easy target.

```{r plotIndvSubjRT, fig.cap="(ref:indvSubjRT)"}
#Make group RT
groupRT <- behavData %>%
  filter(Search.ACC == 1) %>%
  mutate(Subject = "Average") %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(RT = mean(Search.RT)) %>%
  mutate(RT= ifelse(RT==0,NA,RT))
behavData %>%
  filter(Search.ACC == 1) %>%
  group_by(collapseNFLR,Subject) %>%
  summarise(RT = mean(Search.RT)) %>%
  mutate(RT= ifelse(RT==0,NA,RT)) %>%
  ggplot(., aes(collapseNFLR,RT, colour = Subject, group = Subject)) +
  #geom_line(alpha = 0.5) +
  geom_point() +
  geom_point(data = groupRT, size = 2.5, color = "black") +
  geom_line(data = groupRT, size = 1.5, color = "black") +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Response time (ms)", limits = c(500,1000)) +
  guides(colour=FALSE, group = FALSE) +
  theme_apa()
```

(ref:groupRTbyChoice) Participant response times as a fucntion of easy target set size, separated by whether participants chose to respond to the easy or the difficult target. Shading represents standard error.

```{r groupRTByChoice, fig.cap="(ref:groupRTbyChoice)"}
behavData %>%
  filter(Search.ACC == 1) %>%
  mutate(Choice = ifelse(ChoseEasy == 1,"Chose Easy", "Chose Difficult")) %>%
  group_by(collapseNFLR, Choice) %>%
  summarise(mean = mean(Search.RT), se=sd(Search.RT)/sqrt(length(Search.RT))) %>%
  mutate(RT= ifelse(mean==0,NA,mean)) %>%
  ggplot(., aes(collapseNFLR, mean, colour = Choice, group = Choice)) +
  geom_ribbon(aes(ymin = mean - se, ymax = mean + se, fill = Choice), alpha = 0.2, colour = NA) +
  geom_line(size = 1) +
  scale_color_manual(values=c("royalblue3", "red1"))+
  scale_fill_manual(values=c("royalblue3", "red1"))+
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Response Time (ms)", limits = c(500,1000)) +
  theme_apa()

```

(ref:indvRTByChoice) Participant response times as a fucntion of easy target set size, separated by whether participants chose to respond to the easy or the difficult target. Group mean in black and individual subjects plotted behind

```{r indvRTbyChoice, fig.cap="(ref:indvRTByChoice)"}
rtData <- behavData %>%
  filter(Search.ACC == 1) %>%
  mutate(Subject = "Average") %>%
  mutate(Choice = ifelse(ChoseEasy == 1,"Chose Easy", "Chose Difficult")) %>%
  group_by(collapseNFLR, Choice, Subject) %>%
  summarise(RT = mean(Search.RT))
behavData %>%
  filter(Search.ACC == 1) %>%
  mutate(Choice = ifelse(ChoseEasy == 1,"Chose Easy", "Chose Difficult")) %>%
  group_by(collapseNFLR, Choice, Subject) %>%
  summarise(RT = mean(Search.RT)) %>%
  ggplot(., aes(collapseNFLR,RT, colour = Subject, group = Subject)) +
  geom_line(alpha = 0.5) + 
  geom_point(data = rtData, size = 2.5, color = "black") + 
  geom_line(data = rtData, size = 1.5, color = "black") +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Response Time (ms)", limits = c(500,1000)) +
  facet_grid(Choice~.) +
  guides(colour=FALSE, group = FALSE) +
  theme_apa()

behavData %>%
  filter(Search.ACC == 1) %>%
  mutate(Choice = ifelse(ChoseEasy == 1,"Chose Easy", "Chose Difficult")) %>%
  group_by(collapseNFLR, Choice, Subject) %>%
  summarise(RT = mean(Search.RT)) %>%
  ggplot(., aes(collapseNFLR,RT, colour = Choice, group = interaction(Subject,Choice))) +
  geom_point(position = position_dodge(width=1))+
  geom_point(data = rtData, size = 2.5) + 
  geom_line(data = rtData, size = 1.5) +
  scale_x_discrete(name ="Number of easy-coloured objects") +
  scale_y_continuous(name ="Response Time (ms)", limits = c(500,1000)) +
  guides(colour=FALSE, group = FALSE) +
  theme_apa()
```

```{r }
aovDat <-behavData %>%
  filter(Search.ACC == 1) %>%
  mutate(Choice = ifelse(ChoseEasy == 1,"Chose Easy", "Chose Difficult")) %>%
  group_by(collapseNFLR, Choice, Subject) %>%
  summarise(RT = mean(Search.RT))
aov <- aov_ez(
  data = aovDat,
  dv = "RT",
  id = "Subject", 
  within = c("collapseNFLR", "Choice")
)
```


\newpage

```{r create_r-references}
r_refs(file = "NP32019_references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
